Measurement Bias from Address Aliasing

### 2016-01-07 paper.tex
Fixed IEEE keyword issue.
Reduced the spacing of caption text.

% paper.tex
% ACM sigmetric format
% Author: L. K. Melhus and R. E. Jensen
%\documentclass{acm_proc_article-sp}
\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text
\usepackage[utf8]{inputenc}
\usepackage{hyperref} % For PDF metadata
%\usepackage{enumitem} % Controlling list styling

@@

% Terms come from a fixed list of predefined terms
%\terms{Measurement, Performance}
% Free to choose keywords, but must be in alphabetical order
\IEEEkeywords{4K address aliasing, BLAS, heap allocators, measurement bias, memory disambiguation, performance counters}

@@

\subsubsection{Manually adjust address offsets}
In some cases it might make sense to explicitly control the memory addresses used, for example forcing some fixed relative offset between input and output pointers.
This can be achieved by exploiting the fact the \texttt{mmap} is in fact guaranteed to be placed at a page boundary, and use that directly instead of \texttt{malloc}.
The following approach can be used to make an anonymous memory mapping with offset \texttt{d} bytes away from page alignment.
\begin{lstlisting}[breaklines=true]
    mmap(NULL, (n + d), PROT_READ | PROT_WRITE, MAP_PRIVATE | MAP_ANONYMOUS, -1, 0) + d;
\end{lstlisting}
The same pointer difference must of course by subtracted before unmapping the memory.

>>>>

% paper.tex
% ACM sigmetric format
% Author: L. K. Melhus and R. E. Jensen
%\documentclass{acm_proc_article-sp}
\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text
\usepackage[utf8]{inputenc}
\usepackage{hyperref} % For PDF metadata
%\usepackage{enumitem} % Controlling list styling
\usepackage[font=small,skip=0pt]{caption}
%http://tex.stackexchange.com/questions/94016/how-to-reduce-space-between-image-and-its-caption

@@

% Terms come from a fixed list of predefined terms
%\terms{Measurement, Performance}
% Free to choose keywords, but must be in alphabetical order
\begin{IEEEkeywords}
4K address aliasing, BLAS, heap allocators, measurement bias, memory disambiguation, performance counters
\end{IEEEkeywords}

@@

\subsubsection{Manually adjust address offsets}
In some cases it might make sense to explicitly control the memory addresses used, for example forcing some fixed relative offset between input and output pointers.
This can be achieved by exploiting the fact the \texttt{mmap} is in fact guaranteed to be placed at a page boundary, and use that directly instead of \texttt{malloc}.
The following approach can be used to make an anonymous memory mapping with offset \texttt{d} bytes away from page alignment.
\begin{lstlisting}[breaklines=true]
    mmap(NULL, (n+d), PROT_READ | PROT_WRITE, MAP_PRIVATE | MAP_ANONYMOUS, -1, 0) +d;
\end{lstlisting}
The same pointer difference must of course by subtracted before unmapping the memory.
